Paraphrasing for Style

### 2012-09-02 paper/paper.tex
fixed a bunch of conflicting information...

Systems capable of paraphrasing text targeting a specific writing style could be useful for a variety of applications.  For example, they could:
\begin{enumerate}
  \item Help authors of technical documents to adhere to appropriate stylistic guidelines.  
  \item Enable average people to better consume information by translating legalese or medical jargon into nontechnical English.  
  \item Benefit educational applications, allowing students to:
    \begin{enumerate}
    \item Access \emph{modern English} versions of works by authors they are studying.
    \item Experiment with writing in the style of an author they are studying.
    \end{enumerate}
\end{enumerate}

In this paper, we investigate the task of automatic paraphrasing techniques that target a particular writing style, focusing specifically on the style of Early Modern English employed by William Shakespeare.
We explored several different methods, all of which rely on techniques from phrase-based MT, but which were trained on different types of parallel monolingual data.  The first engine was trained on the text of Shakespeare’s plays, along with parallel modern English “translations” that were written to help students better understand Shakespeare's work.  
%A parallel corpus is extracted from these modern translations,
%which is then used to train phrase-based translation models which are capable of automatically paraphrasing ordinary sentences into Shakespearean English.  
We also developed several
baseline systems which do not make use of this parallel text and instead rely on manually compiled dictionaries of expressions commonly found in Shakespearean English, or existing
corpora of out-of-domain parallel monolingual text.

@@

To build a phrase table, we scraped a set of 68,709 phrase/word pairs from \url{http://www.shakespeareswords.com/}; 
example dictionary entries are presented in table \ref{dictionary_example}. 
As described in \cite{Koehn00}, we estimate phrase translation probabilities
based on the frequencies of the translation words/phrases in the target language (Shakespearean English).
For instance, if we look at the modern English word \emph{maybe}, our dictionary lists 4 possible Shakespearean translations. 
We obtained the conditional probabilities for each translation according to the n-gram back-off model built from 36 of Shakespeare's 
plays using the SRILM toolkit \cite{Stolcke02}, 
normalizing the probabilities for each source phrase, for example $p(\text{PERCHANGE}|\text{maybe}) = \frac{0.0000790755}{0.00026264791} = 0.30107035689$.
An example is presented in Table \ref{word_frequency}.
This method allows us to estimate reasonable translation probabilities for use in a phrase table, which is used in combination 
with a language model built from the 36 plays, which are then fed into the Moses decoder \cite{Koehn07}.

@@

\subsubsection{Discussion}
Two main trends are evident in Figure \ref{bleupinc}.  First, notice that all of the systems trained using parallel text achieve higher BLEU scores than the unmodified modern
translations.  While the dictionary baseline achieves a competitive PINC score, indicating it is making a significant number of changes to the 
input, its BLEU is lower than that of the modern translations.  Secondly, it seems apparent that the systems whose parameters are tuned using Minimum Error Rate Training
tend to be more conservative, making fewer changes to the input and thus achieving lower PINC scores, while not improving BLEU scores on the test data.  Finally
we note that using the larger target language model seems to yield a slight improvement in BLEU score.

\subsection{Examples}
Several example paraphrases of lines from {\em Romeo and Juliet} and several Hollywood movies, generated by the top performing system according to BLEU and PINC, are presented in table \ref{examples}.

@@

\section{Human Evaluation}
\label{human_evaluation}
Figure \ref{bleupinc} provides some insight into the performance of the various systems, but it is initially unclear how well the BLEU and PINC
automatic evaluation metrics perform when applied to evaluating paraphrases that target a specific style of writing.  BLEU and PINC have previously
been shown to have high correlation with human judgments of semantic adequacy and lexical dissimilarity of paraphrase candidates, 
but the implications of this for the more specialized task of stylistic paraphrasing are unclear.

@@

These results are roughly in line with the automatic evaluation metrics presented in Figure \ref{bleupinc}.  However we also see several important
trends which are not apparent from the automatic evaluation.
Although the video baseline achieves the highest semantic adequacy in the human evaluation, its BLEU score
is significantly lower than 16plays\_36LM on the Sparknotes data.\footnote{
Note that the BLEU score of 16plays\_36LM is significantly lower when evaluated on the Enotes data.  This makes sense, because the 
16 plays come from Sparknotes. This system is not trained on the 7 Enotes plays which, whose modern translations tend
to be slightly different in style.}
It would appear that in this case BLEU is conflating semantic adequacy with writing style.  Although the paraphrases produced 
by the video baseline have high semantic adequacy, their style tends to differ substantially from the reference translations resulting
in fewer ngram matches, and thus a lower BLEU score.

@@

\section{Automatic Metrics Evaluating Writing Style}
While PINC and BLEU do seem useful for automatically evaluating stylistic paraphrases, BLEU tends to conflate the notions of
semantic adequacy with writing style.  When comparing various systems using automatic metrics, it would seem useful
to separate the effects caused by these two distinct criteria.  We would like our automatic evaluation metrics to be able to distinguish
between a system which generates perfect paraphrases which do not match the target style of writing versus a system which
generates sentences in the correct style, but which convey different meaning.

@@

\subsection{Language Model Style Metric}
Another approach is to build a language model from a corpus of text in the target style and a background language model from text outside the style, then apply Bayes' rule to estimate
the posterior probability that a sentence was generated from the target language model:
\begin{eqnarray*}
P(\text{style}=\text{target}|\text{sentence}) 
& = & \frac{P_\text{LM}(\text{sentence}|\text{target}) P(\text{target})}{P(\text{sentence})} \\
& = & \frac{P_\text{LM}(\text{sentence}|\text{target}) \times 0.5}{P_\text{LM}(\text{sentence}|\text{target}) \times 0.5 + P_\text{LM}(\text{sentence}|\text{source}) \times 0.5} \\
& = & \frac{P_\text{LM}(\text{sentence}|\text{target})}{P_\text{LM}(\text{sentence}|\text{target}) + P_\text{LM}(\text{sentence}|\text{source})} \\
\end{eqnarray*}

\subsection{Logistic Regression Style Metric}
We also consider an approach to measuring style which is based on logistic regression as opposed to cosine similarity.
%We also consider a logistic Regression based approach as an alternative to cosine similarity.
Here the idea is to estimate the probability that each
sentence belongs to the target style based on the ngrams it contains, using large corpora of \emph{in domain} and \emph{out-of domain} sentences to learn  parameters of a logistic regression model.

@@

\subsection{Evaluation}
We trained both the logistic regression and cosine similarity evaluation metrics using the original Shakespeare plays and modern translations as
the source and target corpus respectively, then measured Pearson's Correlation Coefficient between the automatic
evaluation metrics and human judgments described in \S \ref{human_evaluation}.  These results are reported in table \ref{correlation}.

@@

PINC, on the other hand has high correlation with judgments on dissimilarity, and is also moderately correlated with human style
judgments.  We believe PINC has some correlation with writing style, because the systems we are evaluating all target Shakespearean English, 
so whenever changes are made to the input, they are likely to make it similar to the target style.
Although PINC has relatively high correlation with human judgments, it is likely not a very useful measure of writing style in practice.
For example, consider a paraphrase system which makes many changes to the input and thus gets a high PINC score, but targets a completely different writing style.

Both the cosine and logistic regression style metrics achieve the highest overall correlation with human writing style judgments, with the logistic regression style score performing best.

@@

For the purposes of this evaluation, 
we make use of the same paraphrase systems previously described, but swap the source and target languages.
Additionally, each system makes use of a language model constructed from the 16 modern translations, with {\em Romeo and Juliet} held out for testing.  
100 lines from {\em Romeo and Juliet} were automatically translated into modern English using each system, and the aligned modern 
translations were used as a reference when computing BLEU.  The results of evaluating each of the automatic evaluation metrics on this
data are presented in Figure \ref{shakespeare_to_modern_automatic}, correlation of the automatic metrics with with human judgments are presented in 
Table \ref{correlation_s2m} and overall average human judgments are presented in Figure \ref{human_judgements_s2m}.

@@

Finally, we applied these automatic evaluation metrics in an investigation into the task of translating Shakespeare's plays into modern English.

We have shown that access to even a small amount of parallel text produces paraphrase systems 
capable of generating a large number of stylistically appropriate paraphrases which preserving the meaning of the input text.  
Our paraphrase systems targeting Shakespearean English could be beneficial for educational applications, for example helping to
make Shakespeare's work accessible to a broader audience.
Future work could investigate stylistic paraphrasing in other domains, such as paraphrasing emails into formal documents, or
translating legal documents into nontechnical English. 
%We plan to translate the remaining 20 of Shakespeare's plays, which could be beneficial to students
%of Shakespeare and also to human translators.

>>>>

Systems capable of paraphrasing text targeting a specific writing style could be useful for a variety of applications.  For example, they could:
\begin{enumerate}
  \item Help authors of technical documents to adhere to appropriate stylistic guidelines.  
  \item Enable non-experts to better consume technical information, for example by translating legalese or medical jargon into nontechnical English.  
  \item Benefit educational applications, allowing students to:
    \begin{enumerate}
    \item Access \emph{modern English} versions of works by authors they are studying.
    \item Experiment with writing in the style of an author they are studying.
    \end{enumerate}
\end{enumerate}

In this paper, we investigate the task of automatic paraphrasing while targeting a particular writing style, focusing specifically on the style of Early Modern English employed by William Shakespeare.
We explored several different methods, all of which rely on techniques from phrase-based MT, but which were trained on different types of parallel monolingual data.  The first system was trained on the text of Shakespeare’s plays, along with parallel modern English “translations” that were written to help students better understand Shakespeare's work.  
%A parallel corpus is extracted from these modern translations,
%which is then used to train phrase-based translation models which are capable of automatically paraphrasing ordinary sentences into Shakespearean English.  
We also developed several baselines which do not make use of this parallel text and instead rely on manually compiled dictionaries of expressions commonly found in Shakespearean English, or existing
corpora of out-of-domain parallel monolingual text.

@@

To build a phrase table, we scraped a set of 68,709 phrase/word pairs from \url{http://www.shakespeareswords.com/}; 
example dictionary entries are presented in table \ref{dictionary_example}. 
As described in \cite{Koehn00}, we estimate phrase translation probabilities
based on the frequencies of the translation words/phrases in the target language (Shakespearean English).
For instance, if we look at the modern English word \emph{maybe}, our dictionary lists 4 possible Shakespearean translations. 
We obtained the probabilities for each translation according to the n-gram back-off model built from 36 of Shakespeare's 
plays using the SRILM toolkit \cite{Stolcke02}, 
normalizing the probabilities for each source phrase, for example $p(\text{PERCHANGE}|\text{maybe}) = \frac{0.0000790755}{0.00026264791} = 0.30107035689$.
An example is presented in Table \ref{word_frequency}.
This method allows us to estimate reasonable translation probabilities for use in a phrase table, which is used in combination 
with a language model built from the 36 plays, which are then fed into the Moses decoder \cite{Koehn07}.

@@

\subsubsection{Discussion}
Two main trends are evident in Figure \ref{bleupinc}.  First, notice that all of the systems trained using parallel text achieve higher BLEU scores than the unmodified modern
translations.  While the dictionary baseline achieves a competitive PINC score, indicating it is making a significant number of changes to the 
input, its BLEU is lower than that of the modern translations.  Secondly, it seems apparent that the systems whose parameters are tuned using Minimum Error Rate Training
tend to be more conservative, making fewer changes to the input and thus achieving lower PINC scores, while not improving BLEU on the test data.  Finally
we note that using the larger target language model seems to yield a slight improvement in BLEU score.

\subsection{Examples}
Example paraphrases of lines from {\em Romeo and Juliet} and several Hollywood movies, generated by the top performing system according to BLEU and PINC, are presented in table \ref{examples}.

@@

\section{Human Evaluation}
\label{human_evaluation}
Figure \ref{bleupinc} provides some insight into the performance of the various systems, but it is initially unclear how well the BLEU and PINC
automatic evaluation metrics perform when applied to paraphrases that target a specific style of writing.  BLEU and PINC have previously
been shown to have high correlation with human judgments of semantic adequacy and lexical dissimilarity of paraphrase candidates, 
but the implications of this for the more specialized task of stylistic paraphrasing are unclear.

@@

These results are roughly in line with the automatic metrics presented in Figure \ref{bleupinc}.  However we also see several important
trends which are not apparent from the automatic evaluation.
Although the video baseline achieves the highest semantic adequacy in the human evaluation, its BLEU score
is significantly lower than 16plays\_36LM on the Sparknotes data.\footnote{
Note that the BLEU score of 16plays\_36LM is significantly lower when evaluated on the Enotes data.  This makes sense, because the 
16 plays come from Sparknotes. This system is not trained on the 7 Enotes plays which, whose modern translations tend
to be slightly different in style.}
It would appear that in this case BLEU is conflating semantic adequacy with writing style.  Although the paraphrases produced 
by the video baseline have high semantic adequacy, their style tends to differ substantially from the reference translations resulting
in fewer ngram matches, and thus a lower BLEU score.

@@

\section{Automatic Metrics Evaluating Writing Style}
While PINC and BLEU do seem useful for automatically evaluating stylistic paraphrases, BLEU tends to conflate the notions of
semantic adequacy with writing style.  When comparing various systems using automatic metrics, it would seem useful
to separate the effects caused by these two distinct criteria.  We would like our automatic evaluation metrics to distinguish
between a system which generates perfect paraphrases which do not match the target style of writing versus a system which
generates sentences in the correct style, but which convey different meaning.

@@

\subsection{Language Model Style Metric}
Another approach is to build a language model from a corpus of text in the target style and a background language model from text outside the style, then apply Bayes' rule to estimate
the posterior probability that a sentence was generated from the target language model\footnote{
Here we assume an uninformative prior, that is $P(\text{source}) = P(\text{target}) = 0.5$.
}:
\begin{eqnarray*}
P(\text{style}=\text{target}|\text{sentence}) 
& = & \frac{P_\text{LM}(\text{sentence}|\text{target}) P(\text{target})}{P(\text{sentence})} \\
& = & \frac{P_\text{LM}(\text{sentence}|\text{target}) \times 0.5}{P_\text{LM}(\text{sentence}|\text{target}) \times 0.5 + P_\text{LM}(\text{sentence}|\text{source}) \times 0.5} \\
& = & \frac{P_\text{LM}(\text{sentence}|\text{target})}{P_\text{LM}(\text{sentence}|\text{target}) + P_\text{LM}(\text{sentence}|\text{source})} \\
\end{eqnarray*}

\subsection{Logistic Regression Style Metric}
We also consider an approach to measuring style which is based on logistic regression.
%We also consider a logistic Regression based approach as an alternative to cosine similarity.
Here the idea is to estimate the probability that each
sentence belongs to the target style based on the ngrams it contains, using large corpora of \emph{in domain} and \emph{out-of domain} sentences to learn  parameters of a logistic regression model.

@@

\subsection{Evaluation}
We trained the logistic regression, language model and cosine similarity evaluation metrics using the original Shakespeare plays and modern translations as
the source and target corpus respectively, then measured Pearson's Correlation Coefficient between the automatic
evaluation metrics and human judgments described in \S \ref{human_evaluation}.  These results are reported in table \ref{correlation}.

@@

PINC, on the other hand has high correlation with judgments on dissimilarity, and is also correlated with human style
judgments.  We believe PINC has correlation with writing style, because the systems we are evaluating all target Shakespearean English, 
so whenever changes are made to the input, they are likely to make it similar to the target style.
Although PINC has relatively high correlation with human judgments, it is likely not a very useful measure of writing style in practice.
For example, consider a paraphrase system which makes many changes to the input and thus gets a high PINC score, but targets a completely different writing style.

Both the language model and logistic regression style metrics achieve the highest overall correlation with human writing style judgments, achieving comparable performance.

@@

For the purposes of this evaluation, 
we make use of the same paraphrase systems previously described, but swap the source and target languages.
Additionally, each system makes use of a language model constructed from the 16 modern translations, with {\em Romeo and Juliet} held out for testing.  
100 lines from {\em Romeo and Juliet} were automatically translated into modern English using each system, and the aligned modern 
translations were used as a reference when computing BLEU.  The results of evaluating each of the automatic evaluation metrics on this
data are presented in Figure \ref{shakespeare_to_modern_automatic}, correlation of the automatic metrics with with human judgments are presented in 
Table \ref{correlation_s2m} and average human judgments are presented in Figure \ref{human_judgements_s2m}.

@@

We have shown that access to even a small amount of parallel text produces paraphrase systems 
capable of generating a large number of stylistically appropriate paraphrases while preserving the meaning of the input text.  
Our paraphrase systems targeting Shakespearean English could be beneficial for educational applications, for example helping to
make Shakespeare's work accessible to a broader audience.
Future work could investigate stylistic paraphrasing in other domains, such as paraphrasing emails into formal documents, or
translating legal documents into nontechnical English. 
%We plan to translate the remaining 20 of Shakespeare's plays, which could be beneficial to students
%of Shakespeare and also to human translators.
